Efficient Compilation of High Level Python Numerical Programs with Pythran

### 2014-09-05 doc/papers/cgo2014/paper.tex
Anonymize the paper

\authorinfo{Serge Guelton}
           {T{\'e}l{\'e}com Bretagne}
           {serge.guelton@telecom-bretagne.eu}
\authorinfo{Pierrick Brunet}
           {INRIA/MOAIS}
           {pierrick.brunet@inria.fr}
\authorinfo{Mehdi Amini}
           {SILKAN}
           {mehdi.amini@silkan.com}

>>>>

\authorinfo{\phantom{Serge Guelton}}
{\phantom{T{\'e}l{\'e}com Bretagne}}
{\phantom{serge.guelton@telecom-bretagne.eu}}
\authorinfo{\phantom{Pierrick Brunet}}
{\phantom{INRIA/MOAIS}}
{\phantom{pierrick.brunet@inria.fr}}
\authorinfo{\phantom{Mehdi Amini}}
{\phantom{SILKAN}}
{\phantom{mehdi.amini@silkan.com}}
